\item \websitelink{pairwise-calibration}{Pairwise Calibrated Rewards for Pluralistic Alignment}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://evi-micha.github.io}{E. Micha}, \link{https://seas.harvard.edu/person/itai-shapira}{I. Shapira}, and \link{http://procaccia.info}{A. D. Procaccia}. \\In \textit{Proceedings of the 39th Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, 2025.

\item \websitelink{discrepancy-and-envy}{Online Envy Minimization and Multicolor Discrepancy: Equivalences and Separations}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.alexpsomas.com}{A. Psomas}, \link{https://sites.google.com/view/paritoshverma/}{P. Verma}, and \link{https://www.linkedin.com/in/danielyxie/}{D. Xie}. \\In \textit{Proceedings of the 26th ACM Conference on Economics and Computation (\textbf{EC})}, 2025.

\item \websitelink{flexible-voters}{The Proportional Veto Principle for Approval Ballots}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{http://procaccia.info}{A. D. Procaccia}, and \link{https://www.comp.nus.edu.sg/~warut/}{W. Suksompong}. \\In \textit{Proceedings of the 34th International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, 2025.

\item \websitelink{federated-assemblies}{Federated Assemblies}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{http://procaccia.info}{A. D. Procaccia}, \link{https://www.weizmann.ac.il/math/shapiro/home}{E. Shapiro}, and \link{https://sites.google.com/view/zutot/}{N. Talmon}. \\In \textit{Proceedings of the 39th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, 2025. \\$\bigstar$ \textbf{Oral presentation (4.6\% of submissions)}

\item \websitelink{rlhf-social-choice}{Axioms for AI Alignment from Human Feedback}.\\$(\alpha)$ \link{https://luisegehaijing.github.io}{L. Ge}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://evi-micha.github.io}{E. Micha}, \link{http://procaccia.info}{A. D. Procaccia}, \link{https://seas.harvard.edu/person/itai-shapira}{I. Shapira}, \link{http://vorobeychik.com}{Y. Vorobeychik}, and \link{https://jlwu002.github.io}{J. Wu}. \\In \textit{Proceedings of the 38th Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, 2024. \\$\bigstar$ \textbf{Spotlight presentation (2.1\% of submissions)}

\item \websitelink{social-choice-queries}{Computing Voting Rules with Elicited Incomplete Votes}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://safwanhossain.github.io}{S. Hossain}, and \link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}. \\In \textit{Proceedings of the 25th ACM Conference on Economics and Computation (\textbf{EC})}, 2024.

\item \websitelink{ef-beyond-additive}{On the Existence of Envy-Free Allocations Beyond Additive Valuations}.\\$(\alpha)$ \link{http://www.gerdusbenade.com}{G. Benadè}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.alexpsomas.com}{A. Psomas}, and \link{https://sites.google.com/view/paritoshverma/}{P. Verma}. \\In \textit{Proceedings of the 25th ACM Conference on Economics and Computation (\textbf{EC})}, 2024.

\item \websitelink{metric-distortion-with-queries}{Metric Distortion with Elicited Pairwise Comparisons}.\\$(\alpha)$ \link{https://ebadian.org}{S. Ebadian}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://evi-micha.github.io}{E. Micha}. \\In \textit{Proceedings of the 33rd International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, 2024.

\item \websitelink{twitter}{Optimal Engagement-Diversity Tradeoffs in Social Media}.\\$(\alpha)$ \link{https://www.mpib-berlin.mpg.de/staff/fabian-baumann}{F. Baumman}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.rahwan.me}{I. Rahwan}, \link{https://seas.harvard.edu/person/itai-shapira}{I. Shapira}, \link{http://procaccia.info}{A. D. Procaccia}, and \link{https://scholar.google.de/citations?user=7EWrVYIAAAAJ&hl=en}{M. Wüthrich}. \\In \textit{Proceedings of the 33rd ACM Web Conference (\textbf{WWW})}, 2024.

\item \websitelink{strategy-proof-beliefs}{Strategyproof Voting under Correlated Beliefs}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.linkedin.com/in/rachelxli/}{R. Li}, and \link{http://procaccia.info}{A. D. Procaccia}. \\In \textit{Proceedings of the 37th Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, 2023.

\item \websitelink{smoothed-analysis}{Smoothed Analysis of Social Choice Revisited}.\\$(\alpha)$ \link{https://sites.google.com/andrew.cmu.edu/baileyflanigan/home}{B. Flanigan}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.alexpsomas.com}{A. Psomas}. \\In \textit{Proceedings of the 19th Conference on Web and Internet Economics (\textbf{WINE})}, 2023.

\item \websitelink{liquid-defense}{In Defense of Liquid Democracy}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.cs.cornell.edu/home/halpern/}{J. Y. Halpern}, \link{https://jadbabaie.mit.edu}{A. Jadbabaie}, \link{https://math.mit.edu/~elmos/}{E. Mossel}, \link{http://procaccia.info}{A. D. Procaccia}, and \link{https://manrev.github.io/manon/}{M. Revel}. \\In \textit{Proceedings of the 24th ACM Conference on Economics and Computation (\textbf{EC})}, 2023.

\item \websitelink{representation-incomplete}{Representation with Incomplete Votes}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://gregorykehne.com}{G. Kehne}, \link{http://procaccia.info}{A. D. Procaccia}, \link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}, and \link{https://scholar.google.de/citations?user=7EWrVYIAAAAJ&hl=en}{M. Wüthrich}. \\In \textit{Proceedings of the 37th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, 2023.

\item \websitelink{dynamic-fair-division}{Dynamic Fair Division with Partial Information}.\\$(\alpha)$ \link{http://www.gerdusbenade.com}{G. Benadè}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.alexpsomas.com}{A. Psomas}. \\In \textit{Proceedings of the 36th Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, 2022.

\item \websitelink{liquid-in-practice}{Liquid Democracy in Practice: An Empirical Analysis of its Epistemic Performance}.\\\link{https://manrev.github.io/manon/}{M. Revel}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://polisci.mit.edu/people/adam-berinsky}{A. Berinsky}, and \link{https://jadbabaie.mit.edu}{A. Jadbabaie}. \\In \textit{Proceedings of the 2nd ACM conference on Equity and Access in Algorithms, Mechanisms, Optimization (\textbf{EAAMO})}, 2022.

\item \websitelink{distortion-top-t}{Distortion in Voting with Top-t Preferences}.\\$(\alpha)$ \link{https://www.cs.toronto.edu/~bor/}{A. Borodin}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.cs.toronto.edu/~latifian/}{M. Latifian}, and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \\In \textit{Proceedings of the 31st International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, 2022.

\item \websitelink{buyers-reveal}{Can Buyers Reveal for a Better Deal?}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://gregorykehne.com}{G. Kehne}, and \link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}. \\In \textit{Proceedings of the 31st International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, 2022.

\item \websitelink{optimal-congress}{How Many Representatives Do We Need? The Optimal Size of an Epistemic Congress}.\\$(r)$ \link{https://manrev.github.io/manon/}{M. Revel}, \link{https://tao-l.github.io}{T. Lin}, and \link{https://daniel-halpern.com}{D. Halpern}. \\In \textit{Proceedings of the 36th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, 2022.

\item \websitelink{distortion-fair-division}{Fair and Efficient Resource Allocation with Partial Information}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern} and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \\In \textit{Proceedings of the 30th International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, 2021.

\item \websitelink{ranked-binary-judgments}{Aggregating Binary Judgments Ranked By Accuracy}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{https://gregorykehne.com}{G. Kehne}, \link{https://dominik-peters.de}{D. Peters}, \link{http://procaccia.info}{A. D. Procaccia}, \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}, and \link{https://duch.mimuw.edu.pl/~ps219737/}{P. Skowron}. \\In \textit{Proceedings of the 35th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, 2021.

\item \websitelink{binary-mnw}{Fair Division with Binary Valuations: One Rule to Rule Them All}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern}, \link{http://procaccia.info}{A. D. Procaccia}, \link{https://www.alexpsomas.com}{A. Psomas}, and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \\In \textit{Proceedings of the 16th Conference on Web and Internet Economics (\textbf{WINE})}, 2020.

\item \websitelink{optimal-metric-distortion}{Resolving the Optimal Metric Distortion Conjecture}.\\$(\alpha)$ \link{https://www.cs.drexel.edu/~gkatz/}{V. Gkatzelis}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \\In \textit{Proceedings of the 61st Annual IEEE Symposium on Foundations of Computer Science (\textbf{FOCS})}, 2020. \\$\bigstar$ \textbf{Invited to the EC 2021 plenary session: Highlights Beyond EC}

\item \websitelink{fair-division-subsidy-full}{Fair Division with Subsidy}.\\$(\alpha)$ \link{https://daniel-halpern.com}{D. Halpern} and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \\In \textit{Proceedings of the 12th International Symposium on Algorithmic Game Theory (\textbf{SAGT})}, 2019.

